---
output: cynkratemplate::readme_document
---

<!-- README.md and index.md are generated from README.Rmd.
     Edit that file and render it the usual way: rmarkdown::render(),
     devtools::build_readme(), or the Knit button. The cynkratemplate
     package must be installed; it supplies the output format. -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)

# The fixtures below are recorded as printed text, so the print width is baked
# into them. Pin it, or a maintainer whose console is not 80 columns wide
# reflows every line of the recording the next time it is refreshed.
options(width = 80)

pkgload::load_all()

# This README shows a process's memory map, which is different on every run:
# the addresses are randomised by ASLR, and the regions depend on the machine
# and on what R has loaded. Rendering it live would make every render a diff,
# so the output below is a recording, replayed from README-fixtures/.
#
# To refresh the recording, render with the environment variable set:
#
#     PROCMAPS_RECORD=1 Rscript -e 'rmarkdown::render("README.Rmd")'
#
# and commit the changed fixtures along with the README.
recording <- function(name, produce, n = Inf) {
  path <- file.path("README-fixtures", name)
  if (nzchar(Sys.getenv("PROCMAPS_RECORD"))) {
    writeLines(utils::head(produce(), n), path)
  }
  readLines(path)
}

replay <- function(...) cat(recording(...), sep = "\n")
```

# procmaps

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://lifecycle.r-lib.org/articles/stages.html)
[![R build status](https://github.com/r-prof/procmaps/workflows/rcc/badge.svg)](https://github.com/r-prof/procmaps/actions)
[![Codecov test coverage](https://codecov.io/gh/r-prof/procmaps/graph/badge.svg)](https://app.codecov.io/gh/r-prof/procmaps/tree/main)
[![CRAN status](https://www.r-pkg.org/badges/version/procmaps)](https://CRAN.R-project.org/package=procmaps)
<!-- badges: end -->

The goal of procmaps is to help determine which library or other region is mapped to a specific address of a process.
It is the equivalent of `/proc/self/maps` as a data frame, and is designed to work on all major platforms.

## Goals and non-goals

procmaps aims to:

- Return the address space map of the running process as a data frame, one row per mapped region,
  with the columns `/proc/self/maps` exposes: `from`, `to`, `perms`, `offset`, `inode` and `pathname`.
- Give the same answer on every major platform, including those that have no `/proc/self/maps`,
  by way of the bundled gperftools code.
- Install anywhere without setup: no `./configure` step, no `SystemRequirements`, and no package that must be imported.
- Stay small enough to depend on: two exported functions, `procmap_get()` and `path_is_libr()`.

It is explicitly not trying to:

- Map any process other than the one that calls it.
- Turn an address into a function name or a source location.
  It reports the region an instruction pointer falls into, and the file mapped there.
- Take the backtrace or the profile that produced those instruction pointers in the first place.
- Interpret the map beyond `path_is_libr()`, which matches the basename of R's own library.
- Require tibble: it is used when installed, and `as_tibble = FALSE` always returns a plain data frame.

## Installation

You can install the released version of procmaps from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("procmaps")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("pak")
pak::pak("r-prof/procmaps")
```

## Example

This is what the kernel exposes for this R process on Linux, truncated to its first few regions:

``` r
cat(readLines("/proc/self/maps"), sep = "\n")
```

```{r maps-raw, echo = FALSE, comment = ""}
replay("proc-self-maps.txt", function() readLines("/proc/self/maps"), n = 12)
```

Other operating systems make this information available in other form.
This package provides the equivalent as a data frame, regardless of operating system:

``` r
library(procmaps)
procmap_get(as_tibble = TRUE)
```

```{r maps-df, echo = FALSE}
# `as_tibble = TRUE` is what the shown code passes, so the recording is exactly
# what a reader gets. Called without it, procmap_get() emits a "Converting to
# tibble" message once per session, which no recording can reproduce faithfully.
replay("procmap-get.txt", function() {
  utils::capture.output(print(procmap_get(as_tibble = TRUE)))
})
```

Both outputs above are recordings of the same R process, taken on x86_64 Linux under R 4.5.3 and replayed from `README-fixtures/`,
so the addresses in the two views correspond.
The one exception is `[heap]`, which ends higher in the second view,
because `procmap_get()` allocates between the two snapshots and the heap grows.
A live run would differ on every render, because the addresses are randomised and the mapped regions depend on the machine.

---

## Code of Conduct

Please note that the procmaps project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
