---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
pkgload::load_all()
```

# procmaps

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/procmaps)](https://CRAN.R-project.org/package=procmaps)
<!-- badges: end -->

The goal of procmaps is to help determine which library or other region is mapped to a specific address of a process.
It is the equivalent of `/proc/self/maps` as a data frame, and is designed to work on all major platforms.


## Installation

You can install the released version of procmaps from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("procmaps")
```

## Example

This is what `/proc/self/maps` looks like (on Linux) when this document is rendered:

```{bash}
cat /proc/self/maps
```

Other operating systems make this information available in other form.
This package provides the equivalent as a data frame, regardless of operating system:

```{r}
library(procmaps)
procmap_get()
```
